Procurements of the Canadian Government, Runaway Military Contracts

### 2024-12-02 paper/paper.qmd
fixed table and cleaned up intro

Contract: A few words detailing  a brief description of what the contract signed was for

Buyer: The name of government department who awarded the contract

Supplier: The name of the company that fulfilled the contract by agreeing to provide the good or service to the Buyer

Amount: The value of the contract in Canadian Dollars

Award Date: The day the Buyer awarded the contract to the supplier

Start Date: When the contract is due to start

End Date: When the contract is due to end

I derived three additional variables using the IJF variables:

Baseline Days: Number of days since 1st January 2020

Duration Days: End Date subtracted from the Start Date to calculate the duration of the contract

Processed Supplier: The name of suppliers regularized to allow for aggregation and comparison

Baseline Days and Duration Days are used as predictors in the linear model, as Dates are not valid entries into a linear model.

@@

Here is the head of the data that was used in this analysis for a sense of what these variables represent. 
TODO Fix table
```{r fig-head}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

df_table <- df %>% select(-contract, -start_date, -end_date, -link, -duration_days, -per_day, -processed_supplier)

kable(head(df_table, 5), caption = "Sample of the Data") %>%
  kable_styling(font_size = 10, latex_options = c("scale_down"))

>>>>

- **Contract**: A few words detailing a brief description of what the contract signed was for.
- **Buyer**: The name of the government department who awarded the contract.
- **Supplier**: The name of the company that fulfilled the contract by agreeing to provide the good or service to the Buyer.
- **Amount**: The value of the contract in Canadian Dollars.
- **Award Date**: The day the Buyer awarded the contract to the supplier.
- **Start Date**: When the contract is due to start.
- **End Date**: When the contract is due to end.

The head of the IFJ Database:

```{r fig-head1}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center
#| fig-pos: "H"

df_table1 <- df %>%
  select(
    Contract = contract,
    Buyer = buyer,
    Supplier = supplier,
    Amount = amount,
    `Award Date` = award_date,
    `Start Date` = start_date,
    `End Date` = end_date
  )

df_table1_truncated <- df_table1 %>%
  mutate(across(where(is.character), ~ str_trunc(., 15, side = "right", ellipsis = "...")))

# Display the first table
kable(head(df_table1_truncated, 5), caption = "Sample of the Data - Part 1") %>%
  kable_styling(
    font_size = 10,
    latex_options = c("scale_down")
  )

Additional Derived Variables:

- **Baseline Days**: Number of days since 1st January 2020.
- **Duration Days**: End Date subtracted from the Start Date to calculate the duration of the contract.
- **Processed Supplier**: The name of suppliers regularized to allow for aggregation and comparison.

```{r fig-head2}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center
#| fig-pos: "H"

df_table2 <- df %>%
  select(
    `Baseline Days` = baseline_days,
    `Duration Days` = duration_days,
    `Processed Supplier` = processed_supplier
  )

# Truncate character columns if necessary
df_table2_truncated <- df_table2 %>%
  mutate(across(where(is.character), ~ str_trunc(., 15, side = "right", ellipsis = "...")))

# Display the second table
kable(head(df_table2_truncated, 5), caption = "Sample of the Data - Part 2") %>%
  kable_styling(
    font_size = 10,
    latex_options = c("scale_down")
  )

@@
